---
title: "Untitled"
author: "Eva Reindl"
date: "19 11 2020"
output: word_document
---

#INFERENTIAL STATISTICS TRIAL BY TRIAL DATA

```{r}
#PREPARE
R.Version()
rm(list=ls())#removes any other items in your workspace

library(lme4)
library(tidyverse)
source("./functions/diagnostic_fcns.r")
source("./functions/glmm_stability.r")
source("./functions/boot_glmm.r")
source("./functions/drop1_para.r")

```

```{r}
#LOAD DATA
#setwd("C:\\")#sets the working directory, this is where your datafile is
TrayTask <-read.csv("data/Jess_FinalData.csv",header=TRUE, sep = ";")
```

```{r}
#OVERVIEW
str(TrayTask)

#recode variables
TrayTask$Age_group <- as.factor(TrayTask$Age)#this converts a variable classified as continuous into a categorical variable
levels(TrayTask$Age_group)

str(TrayTask)#check whether changes were implemented and if there are any outstanding issues
```

## Postswitch Phase
create a subset for postswitch data
```{r}
postswitch<-subset(TrayTask, Pre_or_postswitch == "post")

postswitch$z.age=as.vector(scale(postswitch$Age_months))#transform age to mean of 0 and SD of 1
mean(postswitch$z.age)#check whether it has worked
sd(postswitch$z.age)
```
```{r eval=FALSE, echo=FALSE}

postswitch$z.trial=scale(postswitch$Trialnr)
str(postswitch)
summary(postswitch)
xx.fe.re=fe.re.tab(fe.model="Success ~ z.age + Relevant_dimension + Condition + 
                      z.trial ",
                   re="(1|Subject_ID)", data=postswitch)
xx.fe.re$summary


```
```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
post.mod<-glmer(Success ~ (z.age+I(z.age^2)) * Relevant_dimension * Condition + 
                      z.trial + 
                      (1+z.trial|Subject_ID), family = binomial, data=postswitch,control=contr)

summary(post.mod)

drop1(post.mod, test = "Chisq")

```



```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
post.mod<-glmer(Success ~ ((z.age+I(z.age^2)) : Relevant_dimension : Condition)^2 + 
                      z.trial + 
                      (1+z.trial|Subject_ID), family = binomial, data=postswitch,control=contr)

summary(post.mod)

drop1(post.mod, test = "Chisq")

```



```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
post.mod<-glmer(Success ~ (z.age+I(z.age^2))*Condition + Relevant_dimension+
                      z.trial + 
                      (1+z.trial|Subject_ID), family = binomial, data=postswitch,control=contr)

summary(post.mod)

drop1(post.mod, test = "Chisq")

```

```{r}
contr<-glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
post.mod<-glmer(Success ~ (z.age+I(z.age^2)) + Relevant_dimension + Condition + 
                      z.trial + 
                      (1+z.trial|Subject_ID), family = binomial, data=postswitch,control=contr)

summary(post.mod)

drop1(post.mod, test = "Chisq")

```





######################Stop here########################

Assess model diagnostics
1) Absence of collinearity
```{r}
post.mod.lm<-lm(Success ~ I(z.age^2) + Relevant_dimension + Condition + Trialnr, data=postswitch)
library(car)
vif(post.mod.lm)
```

#####Model stability
???

Testing the full model
```{r}
post.mod.null<-glmer(Success ~ 1 + Trialnr + (1|Subject_ID), family = binomial, data=postswitch, control=contr)

anova(post.mod.null, post.mod, test="Chisq")

summary(post.mod)
```


Explore significance of fixed effects:
1. 3-way-interaction
```{r}
post.mod.nointer<-glmer(Success ~ I(z.age^2) + Relevant_dimension + Condition + 
                      I(z.age^2):Condition + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

anova(post.mod.nointer, post.mod, test="Chisq")#n.s.
```

We then create a new full model without the three-way interaction.
```{r}
post.mod<-glmer(Success ~ I(z.age^2) + Relevant_dimension + Condition + 
                      I(z.age^2):Condition + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

anova(post.mod.null, post.mod, test="Chisq") # this  explains the data significantly better than a null model
```

test for effect of interactions
1. age:condition
```{r}
post.mod.noagecond<-glmer(Success ~ I(z.age^2) + Relevant_dimension + Condition + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

anova(post.mod.noagecond, post.mod, test="Chisq")
```

We now formulate a new full model, without any of the interactions tested above.
```{r}
library(lme4)
post.mod<-glmer(Success ~ z.age+I(z.age^2) + Relevant_dimension + Condition + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

summary(post.mod)

anova(post.mod.null, post.mod, test="Chisq")
```

Test of significance of terms
1)effect of age?
```{r}
post.mod.noage<-glmer(Success ~ Relevant_dimension + Condition + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

anova(post.mod.noage, post.mod, test="Chisq")
```



2)effect of condition?
```{r}
post.mod.nocond<-glmer(Success ~ I(z.age^2) + Relevant_dimension + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

anova(post.mod.nocond, post.mod, test="Chisq")
```



3)effect of relevant dimension?
```{r}
post.mod.noreldim<-glmer(Success ~ I(z.age^2) +  Condition + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

anova(post.mod.noreldim, post.mod, test="Chisq")
```



4)effect of trial number?
```{r}
post.mod.notrialn<-glmer(Success ~ I(z.age^2) + Relevant_dimension + Condition + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

anova(post.mod.notrialn, post.mod, test="Chisq")
```


No more terms will be removed from the model, so we have found our final model.
```{r}
#effect sizes/CIs
se <- sqrt(diag(vcov(post.mod)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(post.mod), 
              LL = fixef(post.mod) - 1.96 * se, 
              UL = fixef(post.mod) + 1.96 * se))

#Odds ratios and their confidence intervals
exp(tab)


confint.merMod(object=post.mod)
```

Linear effect of age?
```{r}
post.mod1<-glmer(Success ~ z.age^2 + Relevant_dimension + Condition + 
                      Trialnr + 
                      (1|Subject_ID), family = binomial, data=postswitch,control=contr)

summary(post.mod1)
```